Match point to sources

### 2021-07-19 analysis/SI_figs.Rmd
updated all figures and created supplemental figures. Added placement validation checking scripts.

test <- all_farms_sf %>%
  filter(country == "United States of America")
mapview(test)

@@

for(i in c(1, 2,3, 6)){

@@

  count_green_df <- all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "known location")

@@

  count_yellow_df <-  all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "modeled location, known number of farms")

@@

  count_red_df <- all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "modeled location, estimated number of farms")

@@

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms_i, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank(),
        text=element_text(family="Times New Roman")) +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"),
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c(sprintf("Known location \n n = %s", count_green), sprintf("Modeled location, known number of farms \n n = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n n = %s", count_red))) +
  # scale_color_manual(values = c("forestgreen", "orange1"),
  #                   breaks = c("known location", "modeled location, known number of farms"), labels = c(sprintf("Known location \n n = %s", count_green), sprintf("Modeled location, known number of farms \n n = %s", count_yellow))) + 
    # scale_color_manual(values = c("red3"),
    #                 breaks = c("modeled location, estimated number of farms"), labels = c(sprintf("Modeled locations, estimated number of farms \n n = %s", count_red))) +
  labs(title = sprintf("Supplmentary Figure %s: %s farms", i, spp_group))

@@

# Create marginal plots
# Use geom_density/histogram for whatever you plotted on x/y axis 
plot_x <- axis_canvas(total_map, axis = "x") +
  geom_histogram(data = all_farms_i, aes(X, fill = data_type), bins = 360)  +
  #  geom_vline(xintercept = 135) + # check to make sure it lines up
  coord_sf(xlim = c(-180, 180), expand = FALSE) +
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
plot_x

plot_y <- axis_canvas(total_map, axis = "y") +
  geom_histogram(data = all_farms_i, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
 #  geom_hline(yintercept = 0) + #  check to make sure it lines up
  coord_sf(ylim = c(-58, 73), expand = FALSE) + 
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"))
 # coord_flip() 
plot_y

@@

ggsave(sprintf("analysis/figs/supp_map_fig_%s.jpg", spp_group))

@@

>>>>

test <- all_farms_sf %>%
  filter(country == "United States of America")
mapview(test, zcol = "data_type_2")

test <- all_farms_sf %>%
  filter(iso3c == "MEX")
mapview(test, zcol = "data_type_2")

@@

for(i in 1:6){

@@

    count_type_df <- all_farms_i %>%
    group_by(species_group) %>%
    summarise(n=n())

  count_type <- count_type_df$n

    count_green_df <- all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "known locations")

@@

if(is.empty(count_green) == TRUE){
    count_green = 0
  }

  count_yellow_df <-  all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "modeled locations, known number of farms")

@@

if(is.empty(count_yellow) == TRUE){
    count_yellow = 0
  }

  count_red_df <- all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "modeled locations, estimated number of farms")

@@

if(is.empty(count_red) == TRUE){
    count_red = 0
  }

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms_i, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank(),
        text=element_text(family="Times New Roman"), 
        legend.justification='left',
        legend.direction='horizontal') +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow = ifelse(spp_group %in% c("Bluefin tuna", "Non-shrimp crustaceans"), 1, 2))) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"),
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c(sprintf("Known locations \n N = %s", count_green), sprintf("Modeled locations, known number of farms \n N = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n N = %s", count_red)), drop = FALSE) +
  labs(caption = sprintf("%s: N = %s", spp_group, count_type))

@@

# Create marginal plots
# Use geom_density/histogram for whatever you plotted on x/y axis 
plot_x <- axis_canvas(total_map, axis = "x") +
  geom_histogram(data = all_farms_i, aes(X, fill = data_type), bins = 360)  +
  coord_sf(xlim = c(-180, 180), expand = FALSE) +
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)

plot_y <- axis_canvas(total_map, axis = "y") +
  geom_histogram(data = all_farms_i, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
  coord_sf(ylim = c(-58, 73), expand = FALSE) + 
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
 # coord_flip()

@@

ggsave(sprintf("analysis/si_figs/supp_map_fig_%s.jpg", spp_group))
}

## Make the global map by data type 2 (A,B,C,D,E,F) (Supplementary Figures 7-12)

```{r}
world <- ne_countries(scale = "medium", returnclass = "sf")
class(world)

for(i in c(1:6)){

 # i = 1

  data_type_2_id <- unique(all_farms$data_type_2)[i]

  all_farms_i <- all_farms %>%
    filter(data_type_2 == data_type_2_id)

  count_type_df <- all_farms_i %>%
    group_by(data_type_2) %>%
    summarise(n=n())

  count_type <- count_type_df$n

    count_green_df <- all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "known locations")

if(is.empty(count_green) == TRUE){
    count_green = 0
  }

  count_yellow_df <-  all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "modeled locations, known number of farms")

if(is.empty(count_yellow) == TRUE){
    count_yellow = 0
  }

  count_red_df <- all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "modeled locations, estimated number of farms")

if(is.empty(count_red) == TRUE){
    count_red = 0
  }

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms_i, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank(),
        text=element_text(family="Times New Roman"), 
        legend.justification='left',
        legend.direction='horizontal') +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9) )) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"),
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c(sprintf("Known locations \n N = %s", count_green), sprintf("Modeled locations, known number of farms \n N = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n N = %s", count_red)), drop = FALSE) +
  labs(caption = sprintf("Data type %s: N = %s", data_type_2_id, count_type))

# Create marginal plots
# Use geom_density/histogram for whatever you plotted on x/y axis 
plot_x <- axis_canvas(total_map, axis = "x") +
  geom_histogram(data = all_farms_i, aes(X, fill = data_type), bins = 360)  +
  #  geom_vline(xintercept = 135) + # check to make sure it lines up
  coord_sf(xlim = c(-180, 180), expand = FALSE) +
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
plot_x

plot_y <- axis_canvas(total_map, axis = "y") +
  geom_histogram(data = all_farms_i, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
 #  geom_hline(yintercept = 0) + #  check to make sure it lines up
  coord_sf(ylim = c(-58, 73), expand = FALSE) + 
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
 # coord_flip() 
plot_y

ggsave(sprintf("analysis/si_figs/supp_map_fig_%s.jpg", data_type_2_id))

@@

## Make maps for diagram

First map: 
 - All data type A, and known locations from data type C and D

 Second map: 
 - Unknown locations from B, C, D, E, & F
    - All F
    - All E
    - All B
    - Unknown C
    - Unknown D

**First diagram map**
```{r}

  all_farms_i <- all_farms %>%
    filter(data_type_2 %in% c("A", "C", "D")) %>%
  filter(data_type == "known locations")

    count_green_df <- all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "known locations")

if(is.empty(count_green) == TRUE){
    count_green = 0
  }

  count_yellow_df <-  all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "modeled locations, known number of farms")

if(is.empty(count_yellow) == TRUE){
    count_yellow = 0
  }

  count_red_df <- all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "modeled locations, estimated number of farms")

if(is.empty(count_red) == TRUE){
    count_red = 0
  }

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms_i, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank(),
        text=element_text(family="Times New Roman"),
        legend.justification='left',
        legend.direction='horizontal') +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9))) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"),
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c(sprintf("Known locations \n N = %s", count_green), sprintf("Modeled locations, known number of farms \n N = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n N = %s", count_red)), drop = FALSE)

total_map

# Create marginal plots
# Use geom_density/histogram for whatever you plotted on x/y axis 
plot_x <- axis_canvas(total_map, axis = "x") +
  geom_histogram(data = all_farms_i, aes(X, fill = data_type), bins = 360)  +
  #  geom_vline(xintercept = 135) + # check to make sure it lines up
  coord_sf(xlim = c(-180, 180), expand = FALSE) +
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)

plot_y <- axis_canvas(total_map, axis = "y") +
  geom_histogram(data = all_farms_i, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
 #  geom_hline(yintercept = 0) + #  check to make sure it lines up
  coord_sf(ylim = c(-58, 73), expand = FALSE) + 
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
 # coord_flip()

ggsave("analysis/si_figs/workflow_fig_1.jpg")

**Second diagram map**
```{r}

  all_farms_i <- all_farms %>%
    filter(data_type_2 %in% c("B", "C", "D", "E", "F")) %>%
  filter(data_type != "known locations")

    count_green_df <- all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "known locations")

if(is.empty(count_green) == TRUE){
    count_green = 0
  }

  count_yellow_df <-  all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "modeled locations, known number of farms")

if(is.empty(count_yellow) == TRUE){
    count_yellow = 0
  }

  count_red_df <- all_farms_i %>%
    group_by(data_type) %>%
    summarise(n = n()) %>%
    filter(data_type == "modeled locations, estimated number of farms")

if(is.empty(count_red) == TRUE){
    count_red = 0
  }

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms_i, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank(),
        text=element_text(family="Times New Roman"),
        legend.justification='left',
        legend.direction='horizontal') +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9))) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"),
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), labels = c(sprintf("Known locations \n N = %s", count_green), sprintf("Modeled locations, known number of farms \n N = %s", count_yellow), sprintf("Modeled locations, estimated number of farms \n N = %s", count_red)), drop = FALSE)

total_map

# Create marginal plots
# Use geom_density/histogram for whatever you plotted on x/y axis 
plot_x <- axis_canvas(total_map, axis = "x") +
  geom_histogram(data = all_farms_i, aes(X, fill = data_type), bins = 360)  +
  #  geom_vline(xintercept = 135) + # check to make sure it lines up
  coord_sf(xlim = c(-180, 180), expand = FALSE) +
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)

plot_y <- axis_canvas(total_map, axis = "y") +
  geom_histogram(data = all_farms_i, aes(y = Y, fill = data_type), bins = 180, orientation = "y") +
 #  geom_hline(yintercept = 0) + #  check to make sure it lines up
  coord_sf(ylim = c(-58, 73), expand = FALSE) + 
  scale_fill_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known locations", "modeled locations, known number of farms", "modeled locations, estimated number of farms"), drop = FALSE)
 # coord_flip()

ggsave("analysis/si_figs/workflow_fig_2.jpg")

### 2021-07-19 analysis/match_data_sources.Rmd
updated all figures and created supplemental figures. Added placement validation checking scripts.

all_farms <- readRDS("data/all_modeled_marine_farms_31km.rds") %>%
  left_join(all_farms_to_place) %>%
    mutate(data_type = case_when(
    source == "real" ~ "known location", 
    source == "modeled" & estimated == 0 ~ "modeled location, known number of farms",
    source == "modeled" & estimated == 1 ~ "modeled location, estimated number of farms"
  )) %>%
  mutate(estimated = ifelse(is.na(estimated), 0, estimated))

@@

# read in our sources spreadsheet (manually uploaded by GC)
sources <- read_csv("analysis/data/mariculture_mapping_sources.csv") %>%
  clean_names() %>%
  mutate(type = case_when(species == "Salmonids" ~ "salmon",
                          species == "Unfed or algae fed shellfish" ~ "bivalve",
                          species == "Shrimp" ~ "shrimp", 
                          species == "Tuna" ~ "tuna", 
                          species == "General Marine Fish" ~ "marine_fish_general", 
                          species == "Crustaceans" ~ "crustaceans")) %>%
mutate(species_group = case_when(species == "Salmonids" ~ "Salmonidae fish",
                          species == "Unfed or algae fed shellfish" ~ "Unfed or algae fed bivalve molluscs",
                          species == "Shrimp" ~ "Shrimps and prawns", 
                          species == "Tuna" ~ "Bluefin tuna", 
                          species == "General Marine Fish" ~ "General marine fish", 
                          species == "Crustaceans" ~ "Non-shrimp crustaceans")) %>% 
  mutate(data_year_number_of_farms = as.character(data_year_number_of_farms)) %>%
  mutate(data_type_2 = case_when(
    known_farms_location > 0 & known_farms_no_location == 0 & estimated_farms == 0 ~ "A",
    known_farms_location == 0 & known_farms_no_location > 0 & estimated_farms == 0 ~ "B",
    known_farms_location > 0 & known_farms_no_location > 0 & estimated_farms == 0 ~ "C",
    known_farms_location > 0 & known_farms_no_location == 0 & estimated_farms > 0 ~ "D",
    known_farms_location == 0 & known_farms_no_location == 0 & estimated_farms > 0 ~ "F",
  )) %>%
  mutate(data_type_2 = ifelse(str_detect(details, "Although"), "E", data_type_2)) %>%
  mutate(data_type_2 = ifelse(iso3c == "IND" & species == "Unfed or algae fed shellfish", "E", data_type_2)) ## fix some mismatches

@@

sources_prod <- sources %>%
  left_join(all_prod, by = c("iso3c", "type")) %>%
  left_join(spp_prod_per_farm) %>% 
  mutate(tonnes_per_farm = case_when(
    data_type_2 %in% c("A", "B", "C") ~ fao_tonnes_production/number_of_total_farms,
    data_type_2 %in% c("D", "F") ~ spp_prod_per_farm,
    data_type_2 %in% c("E") ~ fao_tonnes_production/number_of_total_farms
  )) %>%
  dplyr::select(-country.y, -spp_prod_per_farm) %>%
  rename("country" = "country.x")

@@

## join all farms with sources data 
all_farms_sources <- all_farms %>%
  left_join(sources_prod, by = c("iso3c", "type")) %>%
  mutate(data_source = case_when(
    data_type == "modeled location, known number of farms" ~ datasource_number_of_farms,
    data_type == "modeled location, estimated number of farms" ~ "NA", 
    data_type == "known location" ~ datasource_farm_locations), 
  data_year = case_when(
    data_type == "modeled location, known number of farms" ~ data_year_number_of_farms,
    data_type == "modeled location, estimated number of farms" ~ "NA", 
    data_type == "known location" ~ data_year_farm_locations)) %>%
  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, details, data_source, data_year, tonnes_per_farm, geometry)

@@

all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv")
```

>>>>

all_farms <- readRDS("data/all_modeled_marine_farms_31km.rds") %>%
  left_join(all_farms_to_place) %>%
    mutate(data_type = case_when(
    source == "real" ~ "known locations", 
    source == "modeled" & estimated == 0 ~ "modeled locations, known number of farms",
    source == "modeled" & estimated == 1 ~ "modeled locations, estimated number of farms"
  )) %>%
  mutate(estimated = ifelse(is.na(estimated), 0, estimated))

@@

# read in our sources spreadsheet (manually uploaded by GC)
sources <- read_csv("analysis/data/mariculture_mapping_sources.csv") %>%
  clean_names() %>%
  mutate(type = case_when(species == "Salmonids" ~ "salmon",
                          species == "Unfed or algae fed shellfish" ~ "bivalve",
                          species == "Shrimp" ~ "shrimp", 
                          species == "Tuna" ~ "tuna", 
                          species == "General Marine Fish" ~ "marine_fish_general", 
                          species == "Crustaceans" ~ "crustaceans")) %>%
mutate(species_group = case_when(species == "Salmonids" ~ "Salmonidae fish",
                          species == "Unfed or algae fed shellfish" ~ "Unfed or algae fed bivalve molluscs",
                          species == "Shrimp" ~ "Shrimps and prawns", 
                          species == "Tuna" ~ "Bluefin tuna", 
                          species == "General Marine Fish" ~ "General marine fish", 
                          species == "Crustaceans" ~ "Non-shrimp crustaceans")) %>% 
  mutate(data_year_number_of_farms = as.character(data_year_number_of_farms)) %>%
  mutate(data_type_2 = case_when(
    known_farms_location > 0 & known_farms_no_location == 0 & estimated_farms == 0 ~ "A",
    known_farms_location == 0 & known_farms_no_location > 0 & estimated_farms == 0 ~ "B",
    known_farms_location > 0 & known_farms_no_location > 0 & estimated_farms == 0 ~ "C",
    known_farms_location > 0 & known_farms_no_location == 0 & estimated_farms > 0 ~ "D",
    known_farms_location == 0 & known_farms_no_location == 0 & estimated_farms > 0 ~ "F",
  )) %>%
  mutate(data_type_2 = ifelse(str_detect(details, "Although"), "D", data_type_2)) %>%
  mutate(data_type_2 = ifelse(iso3c == "IND" & species == "Unfed or algae fed shellfish", "E", data_type_2)) ## fix some mismatches

@@

sources_prod <- sources %>%
  left_join(all_prod, by = c("iso3c", "type")) %>%
  left_join(spp_prod_per_farm) %>% 
  mutate(tonnes_per_farm = case_when(
        str_detect(details, "Although") ~ fao_tonnes_production/number_of_total_farms,
    data_type_2 %in% c("A", "B", "C") ~ fao_tonnes_production/number_of_total_farms,
    data_type_2 %in% c("D", "F") ~ spp_prod_per_farm,
    data_type_2 %in% c("E") ~ fao_tonnes_production/number_of_total_farms  )) %>%
  dplyr::select(-country.y, -spp_prod_per_farm) %>%
  rename("country" = "country.x")

@@

## join all farms with sources data 
all_farms_sources <- all_farms %>%
  left_join(sources_prod, by = c("iso3c", "type")) %>%
  mutate(data_source = case_when(
    data_type == "modeled locations, known number of farms" ~ datasource_number_of_farms,
    data_type == "modeled locations, estimated number of farms" ~ "NA", 
    data_type == "known locations" ~ datasource_farm_locations), 
  data_year = case_when(
    data_type == "modeled locations, known number of farms" ~ data_year_number_of_farms,
    data_type == "modeled locations, estimated number of farms" ~ "NA", 
    data_type == "known locations" ~ data_year_farm_locations)) %>%
  dplyr::select(iso3c, country, species_group, species, data_type, data_type_2, details, data_source, data_year, tonnes_per_farm, geometry)

@@

all_farms <- read_csv("all_marine_aquaculture_farms_sources_31km.csv")

test <- all_farms %>%
  filter(iso3c == "IND", str_detect(species_group, "bivalve"))
```
